### 2024-06-22 Thesis.tex
remove extra spacing in the bibliography

@@

\bibitem{Schm94} Schmidt, W.~M. Heights of points on subvarieties of $\mathbb{G}^n_m$~/ W.~M.~{Sch\-midt}~//
London Mathematical Society Lecture Note Series. Issue~235: Number Theory.
Séminaire de~théorie des~nombres de~Paris 1993–94.~— 1996.~— P.~157—187.

\bibitem{Art48} Artin, Е. Galois Theory~/ E.~Artin; London : University of~Notre Dame, 1942, 1944.~— 96~p.~— ISBN: 978-0-486-62342-9.

@@

\bibitem{TsikhSad14} Садыков, Т.~М. Гипергеометрические и~алгебраические функции многих переменных~/ Т.~М.~Садыков, А.~К.~Цих;
Москва : Наука, 2014.~— 408~с.~— ISBN: 978-5-02-039082-9.

@@

\bibitem{Brbk70} Bourbaki, N. Algèbre: Chapitres 1 à~3. Éléments de~mathématique~/ N.~Bourbaki; Berlin : Springer, 2006.~— 652~p.~— ISBN: 978-3-540-33849-9.

\bibitem{ShaII} Shabat, B.~V. Introduction to~complex analysis. Part~II. Functions of~several variables~/ B.~V.~Shabat; Providence : American Mathematical Society, 1992.~— 371~p.~— ISBN: 978-0-8218-1975-3.

@@

\bibitem{Tsikh92} Tsikh, A.~K. Multidimensional Residues and~Their Applications~/ A.~K.~Tsikh; Providence : American Mathematical Society, 1992.~— 188~p.~— ISBN: 978-0-8218-4560-8.

\bibitem{Mil65} Milnor, J. Lectures on~the~H-Cobordism Theorem~/ J.~Milnor; Princeton : Princeton University Press, 1965.~— 124~p.~— ISBN: 978-0-691-65113-2.

\bibitem{MacLane71} MacLane, S. Categories for the~Working Mathematician~/ S.~MacLane; New~York : Springer-Verlag, 1971.~— 262~p.~— ISBN: 978-0-387-90035-3.

\bibitem{HoTTbook} Homotopy Type Theory: Univalent Foundations of Mathematics / The~{Uni\-va\-lent} Foundations Program //
The HoTT Book | Homotopy Type {The\-o\-ry}~: [сайт].~— URL: \url{https://homotopytypetheory.org/book/} (дата обращения: 01.05.2024).

\bibitem{Stong68} Stong, R.~E. Notes on~Cobordism Theory~/ R.~E.~Stong; Princeton : Princeton University Press, 1969.~— 422~p.~— ISBN: 978-0-691-62221-7.

\bibitem{Trim11} Cobordism categories that don’t involve manifolds / T.~Trimble~//
{Math\-Over\-flow}~: [сайт].~— URL: \url{https://mathoverflow.net/a/59696} (дата обращения: 27.06.2022).

\bibitem{Weston} Weston T., An~introduction to~cobordism theory~/ T.~Weston~//
{Stan\-ford} University. School of~Humanities and~Sciences.
The~Department of~{Math\-e\-mat\-ics} : [сайт].~— URL: \url{https://math.stanford.edu/~ralph/morsecourse/cobordismintro%20.pdf} (дата обращения: 23.08.2022).

\bibitem{Lean} Programming Language and Theorem Prover~— Lean : [сайт].~— URL: \url{https://lean-lang.org/} (дата обращения: 01.05.2024).
\end{thebibliography}

>>>>

\patchcmd{\thebibliography}{\leftmargin\labelwidth}{\setlength\leftmargin{0mm}}{}{}
\patchcmd{\thebibliography}{\advance\leftmargin\labelsep}{}{}{}

@@

\bibitem{Schm94} Schmidt, W.~M. Heights of points on subvarieties of $\mathbb{G}^n_m$~/ W.~M.~{Sch\-midt}~//
London Mathematical Society Lecture Note Series. Issue~235: Number Theory.
Séminaire de~théorie des~nombres de~Paris 1993–94.~— 1996.~— P.~157—\allowbreak187.

\bibitem{Art48} Artin, Е. Galois Theory~/ E.~Artin; London~: University of~Notre Dame, 1942, 1944.~— 96~p.~— ISBN: 978-0-486-62342-9.

@@

\bibitem{TsikhSad14} Садыков, Т.~М. Гипергеометрические и~алгебраические функции многих переменных~/ Т.~М.~Садыков, А.~К.~Цих;
Москва~: Наука, 2014.~— 408~с.~— ISBN: 978-5-02-039082-9.

@@

\bibitem{Brbk70} Bourbaki, N. Algèbre: Chapitres 1 à~3. Éléments de~mathématique~/ N.~Bourbaki; Berlin~: Springer, 2006.~— 652~p.~— ISBN: 978-3-540-33849-9.

\bibitem{ShaII} Shabat, B.~V. Introduction to~complex analysis. Part~II. Functions of~several variables~/ B.~V.~Shabat; Providence~: American Mathematical Society, 1992.~— 371~p.~— ISBN: 978-0-8218-1975-3.

@@

\bibitem{Tsikh92} Tsikh, A.~K. Multidimensional Residues and~Their Applications~/ A.~K. Tsikh; Providence~: American Mathematical Society, 1992.~— 188~p.~— ISBN: 978-0-8218-4560-8.

\bibitem{Mil65} Milnor, J. Lectures on~the~H-Cobordism Theorem~/ J.~Milnor; Princeton~: Princeton University Press, 1965.~— 124~p.~— ISBN: 978-0-691-65113-2.

\bibitem{MacLane71} MacLane, S. Categories for the~Working Mathematician~/ S.~MacLane; New~York~: Springer-Verlag, 1971.~— 262~p.~— ISBN: 978-0-387-90035-3.

\bibitem{HoTTbook} Homotopy Type Theory: Univalent Foundations of Mathematics~/ The {Uni\-va\-lent} Foundations Program~//
The HoTT Book | Homotopy Type {The\-o\-ry}~: [сайт].~— URL: \url{https://homotopytypetheory.org/book/} (дата обращения: 01.05.2024).

\bibitem{Stong68} Stong, R.~E. Notes on~Cobordism Theory~/ R.~E.~Stong; Princeton~: Princeton University Press, 1969.~— 422~p.~— ISBN: 978-0-691-62221-7.

\bibitem{Trim11} Cobordism categories that don’t involve manifolds~/ T.~Trimble~//
{Math\-Over\-flow}~: [сайт].~— URL: \url{https://mathoverflow.net/a/59696} (дата обращения: 27.06.2022).

\bibitem{Weston} Weston T., An~introduction to~cobordism theory~/ T.~Weston~//
{Stan\-ford} University. School of~Humanities and~Sciences.
The~Department of~{Math\-e\-mat\-ics}~: [сайт].~— URL: \url{https://math.stanford.edu/~ralph/morsecourse/cobordismintro%20.pdf} (дата обращения: 23.08.2022).

\bibitem{Lean} Programming Language and Theorem Prover~— Lean~: [сайт].~— URL: \url{https://lean-lang.org/} (дата обращения: 01.05.2024).
\end{thebibliography}
